Data Archiving Attitudes

### 2015-05-17 analysis.Rmd
Added an analysis draft file.

---
title: "Preliminary data analysis"
output: html_document
---

## Data pre-processing

Let's take a look at the numbers of responses by response date and publication date. Please keep in mind that the JDAP adoption dates used in the following analysis are approximate.

@@

load("./data/JDAP 2_clean.rda")
load("./data/jdap_dates.rda")

# add the journal info to the main dataset
assert_that( all(d$journal %in% dates$journal) )
d <- left_join(d, dates, by="journal")

@@

d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")

# number of responses by response date and journal policy in 2015
group_by(d, Date=ResponseDate_YQ, policy) %>% dplyr::summarize(N=length(StartDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by response date.")

# number of responses by publication date and journal policy in 2015
group_by(d, Date=PublicationDate_YQ, policy) %>% dplyr::summarize(N=length(PublicationDate)) %>% ggplot(aes(Date, N, color=policy, group=policy))+geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Number of participants by publication date.")

# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.
```

>>>>

---
title: "Data Archiving Attitudes"
author: Heather Piwowar, Pavel Logacev, Todd J. Vision
date: "May 17, 2015"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    keep_md: yes
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
<!-- csl: apa.csl -->
bibliography: bibliography.bib
---

```{r setup, echo=FALSE, include=TRUE}
suppressPackageStartupMessages({
  require(dplyr)
  require(knitr)
  require(RColorBrewer)
})
```

This is the abstract for now.

# Introduction
Some researchers are sceptical regarding data archiving. We conducted a survey in order to find out how the adoption of data archiving policies by journals affects researcher's attitudes towards archiving and sharing data.

# The Survey

<!-- load and prepare data -->

@@

load("./data/JDAP_Survey_Data_Tidy.rda")
load("./data/jdap_dates.rda")
interactive_mode <- FALSE

# add the journal info to the main dataset
assert_that( all(d$journal %in% dates$journal) ) %>% invisible
d <- left_join(d, dates, by="journal")

@@

d$PolicyAdoptedAtPublication <- ifelse(d$DaysPolicyToPublication>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtResponse <- ifelse(d$DaysPolicyToResponse>0, "After JDAP", "Before JDAP")
d$PolicyAdoptedAtPublication[is.na(d$PolicyAdoptedAtPublication)] <- "No JDAP"
d$PolicyAdoptedAtResponse[is.na(d$PolicyAdoptedAtResponse)] <- "No JDAP"
d$PolicyBinary <- ifelse(d$policy=="Required", "JDAP", "No JDAP")
```

The survey was carried out using [Survey Monkey](www.surveymonkey.com). Invitations to participate were sent out to $n$ <!-- TODO: how many? -->
authors by email every month. The average non-response rate was $p$. <!-- TODO: response/non-response rates -->

```{r, message=FALSE,  echo=FALSE, fig.width=5, fig.height=3, fig.cap="Number of invitations and responses by quarter."}
library(ggplot2)
library(dplyr)

#   # number of responses by response date
#   n_by_date <- group_by(d, Date=ResponseDate_YQ) %>% dplyr::summarize(N=length(Date), type="Responses")
#   n_by_date <- n_by_date %>% mutate(type="Invitations", N=Inf) %>% rbind(n_by_date, .)
#   # TODO: Add invitation data for number of invitations, if necessary.
# 
#   p_by_date <- n_by_date %>%  ggplot(aes(Date, N, color=type, group=type))+geom_point()+geom_line()+theme_bw()+theme(axis.text.x=element_text(angle=90,hjust=1))+ylab("Number of invitations and responses")+xlab("Quarter") #+ ggtitle("Number of invitations and responses by quarter.")
#   p_by_date
#
# It seems to make more sense to focus on the publication date for plotting, until it is clear why there are hardly any responses from the second half of 2013.

  n_by_publication_date <- group_by(d, Date=PublicationDate_YQ) %>% dplyr::summarize(N=length(Date), type="Responses")
  n_by_publication_date <- n_by_publication_date %>% mutate(type="Invitations", N=Inf) %>% rbind(n_by_publication_date, .)
  # TODO: Add invitation data for number of invitations, if necessary.

  p_by_publication_date <- n_by_publication_date %>% ggplot(aes(Date, N, fill=type, alpha=type, group=type)) + 
                ylab("Number of invitations and responses")+xlab("Date of Publication")+geom_bar(stat="identity") + # geom_point()+geom_line()
                scale_fill_manual(values=c("blue", "blue"))+scale_alpha_manual(values=c(.5, 1)) + 
                theme(axis.title.y=element_text(size=rel(0.8)), axis.title.x=element_text(size=rel(0.8)), axis.text.x=element_text(angle=90,hjust=1), legend.title=element_blank())
  print(p_by_publication_date)

#   source("src/multiplot.R")
#   multiplot(p_by_date, p_by_publication_date, cols=2)
```
